Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex

We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
0.90, and 0.95, all with a length of $\pi$, and we vary the extensional
rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  
%
In the simulations we mimic the active control algorithm in the microfluidic experiments by
moving the center of the
doublet at each time step so that the stagnation point occurs exactly in
the middle of the doublet.  
%
With this adjustment, the vesicles either
remain as a doublet in the fluid trap centered around the stagnation
point, or the doublet is broken and the vesicles separate from one
another.  In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
snapshots of a fluid trap containing a vesicle doublet of reduced area
$\Delta A = 0.7$ are simulated at different extensional rates.  While
this doublet remains trapped around the stagnation point for all the
considered extensional rates, a doublet with a reduced area of $\Delta A
= 0.8$ is broken with an extensional rate $\chi = 0.1$
(Figure~\ref{fig:extensional4}).  We summarize the reduced areas and
extensional rates that result in a fluid trap in left plot of
Figure~\ref{fig:extensionalPhaseDiagram}. Parameter values with a blue
mark result in a fluid trap and parameter values with a red mark result
in vesicle separation.

>>>>

We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
point can be controlled in an experimental
setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control
algorithm in the microfluidic experiments by moving the center of the
doublet at each time step so that the stagnation point occurs exactly in
the middle of the doublet.  With this adjustment, the vesicles either
remain as a doublet in the fluid trap centered around the stagnation
point, or the doublet is broken and the vesicles separate from one
another.  In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
snapshots of a fluid trap containing a vesicle doublet of reduced area
$\Delta A = 0.7$ are simulated at different extensional rates.  While
this doublet remains trapped around the stagnation point for all the
considered extensional rates, a doublet with a reduced area of $\Delta A
= 0.8$ is broken with an extensional rate $\chi = 0.1$
(Figure~\ref{fig:extensional4}).  We summarize the reduced areas and
extensional rates that result in a fluid trap in left plot of
Figure~\ref{fig:extensionalPhaseDiagram}. Parameter values with a blue
mark result in a fluid trap and parameter values with a red mark result
in vesicle separation.
